Top Text

### 2022-12-12 Paper.tex
Fixed subsubsections
Rewrote secondary rq

\documentclass[]{report}
\renewcommand\thesection{\arabic{section}}%for page numbering in arabics
\usepackage{graphicx,tabularx}%for figures and tables
\usepackage[utf8]{inputenc} %allows special characters such as ä, ö, ỳ
\usepackage[english]{babel}  %set the language to English
\usepackage[margin=1.5in]{geometry} %change page margins 
\usepackage{sectsty}%section headers
\allsectionsfont{\sffamily\large}
\subsectionfont{\sffamily\normalsize}
\linespread{1.2}% line distance
\usepackage{lipsum}% http://ctan.org/pkg/lipsum
\usepackage{caption}%use for captions on tables
%use this exact command. The style and bibliographystyle has to be authoryear (Havard). The sorting is nyt: name, year, title so that the bibliography is sorted alphabetically. firstinits=true shortens the names: Albert Einstein -> A. Einstein
\usepackage[backend=bibtex,style=authoryear,bibstyle=authoryear,sorting=nyt,firstinits=true]{biblatex}
\setlength\parindent{0pt}%include this so that your paragraphs don't indent automatically
\addbibresource{report.bib} %this attaches your bib-file, your bibliography (must be in the same folder)
\usepackage[compact]{titlesec}%include title formatting package
\usepackage[section]{placeins}
\usepackage{placeins}

@@

A research paper was published on the nineteenth of February 2020 called: "A survey and taxonomy of adversarial neural networks for text-to-image synthesis" that makes use of surveys to compare models for text-to-image generations. This paper aimed to show which text-to-image technique yielded the most realistic results in a wide variety of categories. One issue with this paper was that is was written before the explosion of consumer text-to-image generators happened, which is why we will instead focus on modern consumer-grade generators which are available today. Another issue is that they don't allow average inexperienced artists to use their tools, instead their results are created by the researchers themselves. Because of this their results do not reflect what the average inexperienced artist can expect when using these text-to-image techniques.

@@

Another question we take a look at is which applications have access to the most tools. More tools allow the artist more freedom to improve their results in a multitude of ways. Take for example inpainting, both Dall-E and stable diffusion give the artist access to this. With inpainting you can select, or paint over, a part of an image, you can then tell the generator what you would like to have generated in the selected area. More tools may sound great, however in practice inexperienced artists may struggle to get the hang of these kinds of tools.

@@

\begin{figure}[!htb]
	\centering
	\includegraphics[width=1\linewidth]{TrendsPlotWithLegend}
	\caption{Results from Google Trends showing the popularity of different text-to-image applications}
	\label{fig:TrendsPlotWithLegend}
\end{figure}

We expect the best text-to-image generator out of the four we chose to be stable diffusion. This is due to the fact that stable diffusion offers its users more tools and techniques like inpainting (allows you to regenerate a specific area of an image without regenerating the whole image), this allows the user more freedom to fine-tune their result. Given enough time this will yield a more accurate result. This however only applies for artists who are already experienced, because it can take quite some practice to get used to all the tools that are available in stable diffusion. We expect inexperienced artists to struggle finding the right settings because of the amount of freedom they get. In the case of a completely inexperienced artist, they might find Dall-E easier to use because it can create photo-realistic results without having to fine tune any settings apart from the prompt.

@@

	In order to find out which is the best one, we will look at two things, namely: their accuracy in recreating an image, and their ease of use for inexperienced artists.

	Our x value is the array of different applications that we use and the y value is the result of that (the distance) for each iteration on the road to trying to recreate an image using these applications. The intervening variable in this case would be the amount of experience using these applications.

@@

	In terms of our secondary research question this method also gives us insight if we are aware of the techniques each of them use we can notice if there is a pattern of success or failure with each.

@@

	\newpage

>>>>

\documentclass[]{report}
\renewcommand\thesection{\arabic{section}}%for page numbering in arabics
\usepackage{graphicx,tabularx}%for figures and tables
\usepackage[utf8]{inputenc} %allows special characters such as ä, ö, ỳ
\usepackage[english]{babel}  %set the language to English
\usepackage[margin=1.5in]{geometry} %change page margins 
\usepackage{sectsty}%section headers
\allsectionsfont{\sffamily\large}
\subsectionfont{\sffamily\normalsize}
\linespread{1.2}% line distance
\usepackage{lipsum}% http://ctan.org/pkg/lipsum
\usepackage{caption}%use for captions on tables
%use this exact command. The style and bibliographystyle has to be authoryear (Havard). The sorting is nyt: name, year, title so that the bibliography is sorted alphabetically. firstinits=true shortens the names: Albert Einstein -> A. Einstein
\setcounter{secnumdepth}{3}
\setcounter{tocdepth}{3}
\usepackage[backend=bibtex,style=authoryear,bibstyle=authoryear,sorting=nyt,firstinits=true]{biblatex}
\setlength\parindent{0pt}%include this so that your paragraphs don't indent automatically
\addbibresource{report.bib} %this attaches your bib-file, your bibliography (must be in the same folder)
\usepackage[compact]{titlesec}%include title formatting package
\usepackage[section]{placeins}
\usepackage{placeins}
\titleformat*{\subsubsection}{\normalsize\bfseries}

@@

A research paper was published on the nineteenth of February 2020 called: "A survey and taxonomy of adversarial neural networks for text-to-image synthesis" that makes use of surveys to compare models for text-to-image generations. This paper aimed to show which text-to-image technique yielded the most realistic results in a wide variety of categories. One issue with this paper was that is was written before the explosion of consumer text-to-image generators happened, which is why we will instead focus on modern consumer-grade generators which are available today.

@@

Another question we take a look at is what makes an application good for an inexperienced artist. In answering this question we will consider: the tools available to an artist, the difficulty in using these tools, the accuracy in generating images, the learning curve of an application and the speed with which the application can generate images. With these points of consideration it should be possible to score each application on their ease of use, and on their future potential if the artist were to stick with that application.

@@

\begin{figure}[!h]
	\centering
	\includegraphics[width=1\linewidth]{TrendsPlotWithLegend}
	\caption{Results from Google Trends showing the popularity of different text-to-image applications}
	\label{fig:TrendsPlotWithLegend}
\end{figure}

\par\bigskip

We expect the best text-to-image generator out of the four we chose to be stable diffusion. This is due to the fact that stable diffusion offers its users more tools and techniques like inpainting (allows you to regenerate a specific area of an image without regenerating the whole image), this allows the user more freedom to fine-tune their result. Given enough time this will yield a more accurate result. This however only applies for artists who are already experienced, because it can take quite some practice to get used to all the tools that are available in stable diffusion. We expect inexperienced artists to struggle finding the right settings because of the amount of freedom they get. In the case of a completely inexperienced artist, they might find Dall-E or Midjourney easier to use because they can create photo-realistic results without having to fine tune any settings apart from the prompt.

@@

	In order to find out which is the best one, we will first look at the accuracy with which the generator can create images. We will score the accuracy with an API developed by DeepAI which can calculate image similarity.

@@

	In these graphs the x value is the array of different applications that we use and the y value is the result of that (the distance) for each iteration on the road to trying to recreate an image using these applications. The intervening variable in this case would be the amount of experience using these applications.

@@
